Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-02-18 Report/convergence_centralized.tex
updated convergence proof

To prove the convergence of the centralized algorithm in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are to be satisfied by the objective function sequence to prove the convergence of the transmit and the receive beamformers.
\begin{itemize}
	\item[(a)] The function should be coercive and bounded below
	\item[(b)] The feasible set should be a compact set
	\item[(c)] The sequence should be monotonically decreasing for each iteration
	\item[(d)] Uniqueness of the mapping, \textit{i.e}, there should be one-to-one correspondence between the objective value set and the feasible domain.
\end{itemize}
Using \cite[Prop. A.8]{bertsekas1999nonlinear}, the existence of a global minimizer in the feasible set can be guaranteed if the conditions (a) and (b) are satisfied. Since the feasible set is not fixed in each iteration, we require additional conditions (c) and (d) to prove the global convergence of the objective function, the transmit and the receive precoders. Assuming the above conditions are satisfied by the iterative algorithm, using Bolzano-Weierstrass theorem \cite{rudin1964principles}, we can show that any bounded monotonically decreasing sequence has a unique limiting point. Using the property of one-to-one mapping between the feasible domain and the objective value, the transmit and the receive beamformers also approaches to a limiting point since the inverse mapping is unique in each iteration. Note that the relaxed iterative problem has the unique solution but not the original nonconvex problem. Since the transmit precoders in problem in \eqref{eqn-6} and \eqref{eqn-mse-1} are invariant to any unitary rotations due to the absolute value operator in the \ac{SINR} expression, the limiting point is a set of precoder vectors with different unitary rotations. The limiting point of the iterative algorithm is susceptible to the initial operating point due to the linearization of the nonconvex \ac{DC} constraint.

@@

To prove the boundedness, it is enough to show that the objective function is bounded below due to the minimization objective. Since the minimum value of the norm operator is zero, \textit{i.e}, the limiting point is \me{< -\infty}, it is bounded below. Note that the objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded. Note that the norm operator in the objective function is continuous and coercive over the feasible set but not differentiable at its minimum point. Using the conditions (a) and (b) we can guarantee the existence of a minimizer to the original nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.

>>>>

To prove the convergence of the centralized algorithm in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are to be satisfied by the objective function sequence to prove the convergence of the transmit and the receive beamformers.
\begin{itemize}
	\item[(a)] The function should be coercive and bounded below
	\item[(b)] The feasible set should be a compact set
	\item[(c)] The sequence should be monotonically decreasing for each iteration
	\item[(d)] Uniqueness of the mapping, \textit{i.e}, there should be one-to-one correspondence between the objective value set and the feasible domain.
\end{itemize}
Using \cite[Prop. A.8]{bertsekas1999nonlinear}, the existence of a global minimizer in the feasible set can be guaranteed if the conditions (a) and (b) are satisfied. Since the feasible set is not fixed in each iteration, we require additional conditions (c) and (d) to prove the global convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders.

Assuming the above conditions are satisfied by the objective function of the iterative algorithm, using Bolzano-Weierstrass theorem \cite{rudin1964principles}, we can show that any bounded monotonically decreasing sequence has a unique limiting point. The one-to-one mapping between the feasible domain and the objective function value is required to prove the convergence of the transmit and the receive beamformers upon convergence of the objective function value iterates. Note that the relaxed iterative problem has the unique solution but not the original nonconvex problem. Since the transmit precoders in problem in \eqref{eqn-6} and \eqref{eqn-mse-1} are invariant to any unitary matrix rotations due to the absolute value operator in the \ac{SINR} expression, the limiting point is a set of precoder vectors with different phase rotations. The limiting point of the iterative algorithm is susceptible to the initial feasible point, since it is the operating point for linearizing the nonconvex \ac{DC} constraint.

@@

To prove the boundedness, it is enough to show that the objective function is bounded below due to the minimization objective. Since the minimum value of the norm operator is zero, \textit{i.e}, the limiting point is \me{< -\infty}, it is bounded below. Note that the objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded. The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, therefore it is coercive. Note that the norm operator is not differentiable at the minimum point for \me{\ell_1} and \me{\ell_infty}. Using conditions (a) and (b), we can guarantee the existence of a minimizer to the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.

### 2015-02-18 Report/introduction.tex
updated convergence proof

The connection between the achievable capacity and the \ac{MSE} for the received symbol by using the fixed \ac{MMSE} receivers as shown in \cite{mse_duality,christensen2008weighted} can also be used to solve the \ac{WSRM} problem. In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed linearization coefficients. In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders. Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the remaining others are fixed. The \ac{MSE} reformulation for the \ac{WSRM} problem has also been studied in \cite{hong2012decomposition} by using the \ac{SCA} to solve the problem in an iterative manner. Additional rate constraints based on the \ac{QoS} requirements were included in the \ac{WSRM} problem and solved via \ac{MSE} reformulation in \cite{kaleva2013primal,kaleva2013decentralized}.

>>>>

The relation between the achievable capacity and the \ac{MSE} of the received symbol by using fixed \ac{MMSE} receivers can be used to solve the \ac{WSRM} problem \cite{mse_duality}. In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed linearization coefficients. In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders. Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the remaining others are fixed. The \ac{MSE} reformulation for the \ac{WSRM} problem has also been studied in \cite{hong2012decomposition} by using the \ac{SCA} to solve the problem in an iterative manner. Additional rate constraints based on the \ac{QoS} requirements were included in the \ac{WSRM} problem and solved via \ac{MSE} reformulation in \cite{kaleva2013primal,kaleva2013decentralized}.
